### 2025-06-27 Scripts/Manuscript/manuscript.Rmd
Rough First Redraft -Discussion of the Descriptive Version of the study (version 2)

abstract: |
  For a replication to be informative, measurement should be reliable and valid in both original and replication studies. 
  Recent studies have identified problems with measurement and measurement reporting in both original and replication studies, although the association between measurement and replicability remains unclear. 
  We investigated the reliability and measurement reporting of 77 measures within 56 Many Labs replications and related original articles [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many] and studied their association with replicability. 
  We found that not all measures were sufficiently reliable across contexts, and that only few measures were accompanied with reliability and validity evidence. 
  Furthermore, “questionable measurement practices” (QMPs) in replication studies were associated with lower replicability, while original study reliability was not. 
  These results corroborate existing findings that construct validity in published research is often unknown, which may complicate replication research. 
  We offer suggestions on improving measurement practices and argue that reported measurement information should inform the decision to replicate.

keywords          : "reliability, construct validity, measurement, reporting, questionable measurement practices, replicability, credibility, psychology"
wordcount         : "158"

@@

```{r setup, include = FALSE}
# loading R libraries
library(papaja)
library(worcs)
library(tidyr)
library(betareg)
library(lmerTest)
library(psych)
library(forcats)
library(GPArotation)
library(ggplot2)
library(ggridges)
library(GGally)
library(ggforce)
library(grid)
library(gridExtra)
library(metafor)
library(sandwich)
library(lmtest)

# loading source script
source(file = "../source_script.R")

# Code below loads the processed data. The raw data was prepared for analysis in 'prepare_data.R.
load_data()

# creates a reference list for all used R packages and the installed R version (does not automatically include Rstudio)
r_refs("r-references.bib")
```

@@

```{r analysis-preferences}
# Seed for random number generation
set.seed(17042023)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

@@

Findings from psychological research should be credible to build and extend upon them. A credible finding must be replicable [@vazire2022CredibilityReplicabilityImproving], such that the observed effect is sufficiently comparable across the original study and subsequent replications in new samples and using nearly identical designs [@nosek2022replicability]. In this article, we investigate how the credibility of psychological findings relates to problems in psychological measurement and how measurement problems may affect subsequent replications.

Unfortunately, the Reproducibility Project: Psychology [RPP\; @osc2015estimating] and other large-scale replication projects that sought to replicate earlier and seminal findings [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many] typically yielded smaller effects in replications compared to original studies, with Many-Labs projects featuring different locations and samples. In response to this string of failed replications, there was widespread alarm regarding the credibility and robustness of findings in psychological science [@hughes2018psychology; @giner2019crisis], combined with efforts to explain the low replication rate. The factors that have been proposed include questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], and biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science]. Another important factor is the impact of measurement-related challenges on replicability and credibility.

## Credibility & Measurement
Psychological constructs, such as affective states or intelligence, cannot be measured directly. Psychological measurements involve random measurement errors and uncertainties about whether the targeted construct is indeed well reflected in the scores retrieved from the measurement procedure.

Reliability estimates provide an indication of how consistent the responses on a measurement are. Reliability is a critical first step to obtaining credible findings. Because if the scores on a measure are not consistent with themselves, it is unlikely that any effect associated with the measure can credibly be established. Psychometrics offers various ways to assess reliability empirically [@nunnally1978overview; @mellenbergh2011conceptual].

Moreover, researchers cannot claim to have found a credible psychological effect if the measures do not relate to the psychological constructs [@cook2002experimental]. Validity indicates the extent to which a measure measures what it is supposed to measure [@borsboom2004concept] and can be studied by comparing the test scores’ empirical associations to the theoretical associations of the constructs [@cronbach1955construct].

## Replicability & Measurement

Replicability and reliable and valid measurement are essential to the credibility of a finding, and are related to each other. Indeed, recent studies have illustrated that both the reliability of the measure [@stanley2014expectations] and the reporting of information relevant to demonstrating the validity of the measurement [@shaw2020measurement; @flake2017construct; @flake2020measurement] may predict the replicability of psychological findings.

In this study, we investigate the relation of reliability and measurement reporting with replicability, using data and reports from the large-scale Many Labs replication projects. Because the Many Labs projects [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many] are large-scale collaborations in which multiple lab locations directly replicated the same set of studies, their data allows us to study the variability in their measures across different contexts. Furthermore, because the Many Labs projects used preregistered and documented structured protocols, we expect the measurement used in these projects to represent a high standard within the field. Any issues in measurement here might suggest that other replications could face similar or greater challenges.

## Existing Research

### Reliability

Notwithstanding the common yet mistaken belief that reliability is a measure-specific feature, the reliability of a measure typically varies between samples differing in latent trait variance and/or the latent measurement model [@cho2015cronbach; @pauly2018resampling]. Besides random variation due to the sampling error, the variations can also reflect true variation in reliability, also known as reliability heterogeneity [@vacha-haase1998ReliabilityGeneralizationExploring]. For instance, measures will normally show lower reliability in more homogeneous samples than heterogeneous samples [@pike1998reliability], which follows from reliability being a function of the variability in true scores. In modern latent variable modelling, group differences in reliability can also emerge because of failures of measurement invariance across groups (e.g., differences in factor loadings or item difficulty parameters across groups).

Variations in reliability could contribute to the discrepancy between effects in original and replication studies, as well as within replications of the same original effect. After all, it has long been known that measurement error suppresses observed effects and associations [@spearman1904proof]. @stanley2014expectations simulated data of items on a scale based on levels of sampling error and reliability similar to what is standard in psychological research. The results showed that the variation due to measurement error was substantial enough to cause replications of a positive small effect to observe anywhere between a medium negative effect and a large positive effect [@stanley2014expectations]. In summary, studies using unreliable measures are less replicable, even when the measurement is equally reliable between original and replication.

### Measurement Reporting

Despite the importance of reliable and valid measurement, research has shown that Questionable Measurement Practices (QMPs) are not uncommon. QMPs are practices that raise doubts about a measurement’s validity [@flake2020measurement] and have been coined as a term analogous to Questionable Research Practices [QRPs\; @john2012measuring]. QMPs range from lack of transparency and unclear motivation in choice of measure to poor justification for modifications of a measure and procedure of an existing measure [@flake2020measurement]. Specifically, @flake2020measurement identified six key questions that an article should answer to avoid QMPs: the definition of the construct, how and why the measure was selected, how the measure operationalizes the construct, how the measure was quantified, whether it was modified or not and why, and the reasons and details of creating a measure if applicable. If these questions can be answered clearly based on the reported measurement information, then reporting is sufficiently transparent to promote a more cumulative psychological science.

@flake2022construct documented QMPs among 100 replications and their respective original articles from the RPP [@osc2015estimating]. They coded the number of measures, the number of items in the measure, and the information that was reported describing the measure and providing evidence justifying its use. Besides limited reporting of validity and reliability evidence for the coded measures, @flake2022construct found that several of the measures in the RPP did not report the number of items, the response format, or the scoring of the scale. Furthermore, only eight of the 40 translated scales contained validity evidence for the translated version of the scale. Evidence showing that this and other modifications between original and replication did not invalidate the measurement was rarely reported.

Further findings by @flake2022construct and others [@flake2017construct; @shaw2020measurement] also illustrated how QMPs create challenges for replicating researchers. To reconstruct the measurement, replication researchers need to know the items that were used, how they were presented to the subjects, and how to compute the scores. If the measure is not reconstructed exactly, constructs measured by original and replication may differ, possibly creating differences in effect sizes between original and replication studies, resulting in less informative replications.

### Research Contribution

Our study investigates the relation of reliability and measurement reporting with replicability, using data and reports from the large-scale Many Labs replication projects. First, this study expands on the research by  @stanley2014expectations, to see if reliability is related to replication success in empirical replication data. Specifically, we investigate whether successfully replicated studies differed in reliability from non-replicated studies. @stanley2014expectations assumed reliability to be constant across studies, which we know to be an oversimplification. Therefore, to add further context to the relation between reliability and replication, we also investigate the variation in reliability as observed across labs.

Furthermore, we conceptually replicate the study by @flake2022construct on QMPs in replications and original research in the context of the Many Labs projects. We expand on @flake2022construct by exploring associations between QMPs and the replicability of psychological findings.

## Research Questions & Hypotheses

### Reliability

Measurement reliability can vary across samples, because the residual variance or the true variance in the item scores, or both, differs between samples. While differences in these variances across samples is inevitable, these differences should not be systematic between replication and original samples for their results to remain comparable. Therefore, we investigated the reliability in replication (Research Question 1a; RQ1a[^1]) and original psychological research (RQ1b). The Many Labs studies were intended as direct replications, which implies that deviations from the original research should be irrelevant for testing the effect [@nosek2022replicability], including systematic differences in reliability (Hypothesis 1; H1).

[^1]: The numbering of the research questions and hypotheses matches the numbering in the preregistration

Additionally, for the results of direct replications to be comparable with each other, the differences in reliability should be comparable. Systematic differences in reliability could indicate that measurement assesses fundamentally different constructs. Therefore, we investigated  whether reliability estimates differed systematically between replicating labs (RQ2). For effect sizes, there is little empirical evidence of widespread heterogeneity among the Many Labs replications [@klein2018many; @olsson2020heterogeneity]. We expect that there is no systematic variation in the reliability estimates of replications of the same original study (H2) either.

In theory, there should be a positive relation between reliability and replicability. Greater reliability means the variance around the estimate of the true effect is decreased [@nunnally1994assessment]. If the true effect is not null, then the statistical tests with reliable measures are more likely to be significant. To empirically assess this, we investigated the association between replication study reliability and replication outcome (RQ3). We expected that reliability in the replications would be positively associated with replication success (H3).

### Measurement Reporting

We conceptually replicate the findings on measurement reporting of @flake2022construct by documenting the frequency of QMPs in replications of psychological research (RQ4a) and original psychological research (RQ4b). @flake2022construct found that RPP replications contained on average more QMPs than original studies. We hypothesized that for our Many Labs sample, QMPs would be more frequent in original psychological research than in replication research (H4), because the Many Labs replications used structured protocols documenting the measurement.

QMPs obscure information about a particular measurement, which may cause issues when reconstructing that measurement in subsequent replication attempts. Because resulting deviations in measurement may be partly responsible for deviations in replication and original effects [@flake2022construct], we investigated whether QMPs in replication protocols were associated with the replication outcome (RQ5). A reduction in QMPs corresponds to greater transparency in measurement reporting. In line with earlier research finding that other transparency-related practices are associated with more robust estimates of effects [@wicherts2011willingness], we expected QMPs in replications to be negatively associated with replication success (H5).

@flake2022construct proposed that QMPs in original articles may impede recreating measurements for replications, and indeed @shaw2020measurement found evidence for such a spill-over effect with validity. In line with this research, we investigated the association between QMPs in original research and QMPs in replications of psychological research (RQ6). We expected the total number of QMPs in original psychological research to be positively related to the total number of QMPs in replication research (H6).

# Disclosures

### Preregistration

We preregistered data collection, coding protocol, and planned analyses: <https://osf.io/jgxyu>. Deviations from the preregistration are explicitly mentioned in the text.

### Data, Materials, and Online Resources

This manuscript was created in RStudio [*v`r rstudioapi::versionInfo()$version`*\; @R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*\; @vanlissaWORCS2021] to ensure reproducibility and transparency. All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/>.

### Reporting

We report how we determined all data exclusions, all manipulations, and all measures in the study. Our sample size was predetermined by the number of studies in the Many Labs projects.

### Ethical Approval

This research was approved by the Tilburg University School of Social and Behavioral Sciences Ethical Review Board (nr. TSB_TP_REMA06).

@@

## Sample

### Data Source

The data used for the analyses consisted of three main sources: replication datasets, replication protocols, and original study articles. The data came from the Many Labs replication projects. Specifically, data from Many Labs 1, 2, 3, & 5 [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many] was included. Many Labs 4 [@klein2022many] was excluded, as there was no publicly available replication protocol. Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.

### Unit of Analysis

The unit of analysis in this study was a measure of a single psychological construct used in the primary analysis that was targeted in the replication. Multiple psychological constructs could be measured per original study or replication. We used the replication protocols to identify these measures. We did not include acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses.

## Data Collection

We retrieved the data on the replication protocols and replication datasets of Many Labs 1, 2, 3, & 5 from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned to ensure the planned analyses were feasible. However, no coding or analysis of either of them had taken place before we preregistered the analyses. Further details on the search strategy can be found in the [supplementary materials](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) (URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd>).

### Replication Datasets

The replication datasets refer to the publicly available datasets containing the data obtained from all labs partaking in a Many Labs study. For the analyses, we extracted the scores on the items of each previously identified measure that met our inclusion criteria specified below. When scores could not be clearly identified, any available codebooks, analysis scripts, or study materials were used to identify the relevant scores.

To be included in the planned analyses on calculated reliabilities (RQ1, RQ2, and RQ3), the measure had to be a scale consisting of multiple items. If cleaned data were available, we chose these over raw data, to ensure that variables were coded as intended (e.g., no reverse-coded items). We omitted pilot data from the analyses. These criteria resulted in suitable item score data from `r apa_num(nrow(data_h23_avg))` replication sets spread across on average approximately `r apa_num(mean(table(data_h23$g)), digits = 0)` lab locations for the analyses of Hypotheses 2 & 3.

@@

### Saving to Intermediate Data Folder
open_data(data = data_1.3_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_1.3_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_1.3_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_1.3_clean))), ".yml"))

open_data(data = data_1.10_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_1.10_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_1.10_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_1.10_clean))), ".yml"))

open_data(data = data_1.11_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_1.11_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_1.11_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_1.11_clean))), ".yml"))

open_data(data = data_1.12.3.1_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_1.12.3.1_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_1.12.3.1_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_1.12.3.1_clean))), ".yml"))

open_data(data = data_1.12.3.2_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_1.12.3.2_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_1.12.3.2_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_1.12.3.2_clean))), ".yml"))

open_data(data = data_2.10.1_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_2.10.1_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_2.10.1_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_2.10.1_clean))), ".yml"))

open_data(data = data_2.12.1_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_2.12.1_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_2.12.1_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_2.12.1_clean))), ".yml"))

open_data(data = data_2.12.2_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_2.12.2_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_2.12.2_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_2.12.2_clean))), ".yml"))

open_data(data = data_2.12.3_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_2.12.3_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_2.12.3_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_2.12.3_clean))), ".yml"))

open_data(data = data_2.15_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_2.15_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_2.15_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_2.15_clean))), ".yml"))

open_data(data = data_2.20_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_2.20_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_2.20_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_2.20_clean))), ".yml"))

open_data(data = data_2.23_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_2.23_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_2.23_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_2.23_clean))), ".yml"))

open_data(data = data_3.2.1.1_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_3.2.1.1_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_3.2.1.1_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_3.2.1.1_clean))), ".yml"))

open_data(data = data_3.2.1.2_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_3.2.1.2_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_3.2.1.2_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_3.2.1.2_clean))), ".yml"))

open_data(data = data_3.7.1_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_3.7.1_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_3.7.1_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_3.7.1_clean))), ".yml"))

open_data(data = data_3.7.2_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_3.7.2_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_3.7.2_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_3.7.2_clean))), ".yml"))

open_data(data = data_3.8.2_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_3.8.2_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_3.8.2_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_3.8.2_clean))), ".yml"))

>>>>

abstract: |
  For a replication to be informative, measurement should be reliable and valid in both original and replication studies.

keywords          : "reliability, construct validity, measurement, reporting, questionable measurement practices, replications, informative replications, psychology"
wordcount         : "1"

@@

```{r setup, include = FALSE}
# loading R libraries
library(papaja)
library(worcs)
library(lavaan)
library(psych)
library(metafor)
library(forcats)
library(ggplot2)
library(grid)

# loading script with helper functions
# source(file = "../helper_functions.R") !!!needs to still be created

# Code below loads all data. The raw data was loaded within the 'prepare_data.R script.
load_data()

# the code below removes the raw data to preserve disk space.
# If you want to rerun the data cleaning and preparations steps, DO NOT run
# this code.
# If you want to only rerun the analyses, YOU CAN run the code below.
rm(coded_data_initial_raw, coded_data_revised_raw, coded_data_vignette_raw,
   data_2.10.1, data_2.12, data_2.15, data_2.19.1, data_2.2, data_2.20, 
   data_2.23, data_2.3, data_2.4.1, data_2.4.2, data_2.8.2, data_3.5, data_5.1,
   data_5.4, data_5.5, data_5.7, data_5.9.1, data_ml1, data_ml3)

# creates a reference list for all used R packages and the installed R version 
# (does not include Rstudio)
r_refs("r-references.bib")
```

@@

```{r analysis-preferences}
# Seed for random number generation
set.seed(26052025)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r helper_functions}
##### PUT THIS ALL IN A SEPARATE R SCRIPT FILE.

# Function for storing data openly in the intermediate data folder
saving_to_intermediate_data <- function(data){
  open_data(data = data, filename = paste0(paste0(
    "Data/IntermediateData/", deparse(substitute(data))), ".csv"),
    codebook = NULL, value_labels = NULL) 
}

# Function for storing data openly in the analysis data folder
saving_to_analysis_data <- function(data){
  open_data(data = data, filename = paste0(paste0(
    "Data/AnalysisData/", deparse(substitute(data))), ".csv"),
    codebook = NULL, value_labels = NULL) 
}

# function for changing QMP data to their ratio equivalent
Create_QMP_descriptive_case <- function(practice_name, original_coded_var, replication_coded_var){
  # add practice name to first row
  Practice <- practice_name

  # Sum all QMP/GMP (Good Measurement Practice), keeping NA items out of
  # the equation
  original_n_QMPs <- sum(original_coded_var == "FALSE", na.rm = TRUE)
  replication_n_QMPs <- sum(replication_coded_var == "FALSE", na.rm = TRUE)

  original_n_GMPs <- sum(original_coded_var == "TRUE", na.rm = TRUE)
  replication_n_GMPs <- sum(replication_coded_var == "TRUE", na.rm = TRUE)

  # calculating the N of applicable items for originals
  N_applicable_original <- original_n_QMPs + original_n_GMPs

  # checking that we are not dividing by 0, and then calculating the ratio of 
  # QMPs for applicable items for originals
  if(N_applicable_original != 0){
    QMP_percentage_original <- round(original_n_QMPs / (N_applicable_original), 2)
  } else{
    QMP_percentage_original <- 0
  }

  # calculating the N of applicable items for replications
  N_applicable_replication <- replication_n_QMPs + replication_n_GMPs

  # checking that we are not dividing by 0, and then calculating the ratio of 
  # QMPs for applicable items for replications
  if(N_applicable_replication != 0){
    QMP_percentage_replication <- round(replication_n_QMPs / (N_applicable_replication), 2)
  } else{
    QMP_percentage_replication <- 0
  }

  # calculating the Phi coefficient to estimate the relation between variables
  Phi <- phi(matrix(c(original_n_QMPs, original_n_GMPs, replication_n_QMPs, 
                      replication_n_GMPs), nrow = 2, byrow = TRUE))

  return(c(Practice, QMP_percentage_original, N_applicable_original, QMP_percentage_replication, N_applicable_replication, Phi))
}

@@

In psychological research we are often interested in establishing a robust effect involving one or more latent constructs (e.g., IQ and conscientiousness) that describes a psychological phenomenon (like increased conscientiousness causing a person to develop higher IQ). However in the wake of the replication crisis the robustness of effects in psychology has been called into question. The Reproducibility Project: Psychology [RPP\; @osc2015estimating] and other large-scale replication projects [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many] and typically yielded smaller effects in replications compared to original studies. Replicability is one of the key ways to establish the robustness of an effect (Nosek RRR & …). If an effect does not replicate, it is likely not robust. Numerous factors have been proposed to explain why the original effects did not appear robust, including questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science], and more.

These replication efforts and the subsequent lines of research have been of instrumental value in determining the lack of robustness in effects, uncovering what the causes of this lack of robustness are, and spearheading initiatives like … to help improve the robustness of effects. However, robustness was only one aspect of the goal highlighted at the beginning of this article, the other aspect, the fact that the effect should describe a true psychological phenomenon has received relatively less attention, although this is changing (SOME CITATIONS).

In this article, we contribute to the rising research investigating the soundness of measurement in research. After all, a true psychological phenomenon is requires accurate measurement on the relevant constructs. Our aim is to create a greater understanding of the extent to which this. We provide a descriptive account of the measurement reporting practices in the Many Labs replications and related original research, in tandem with the measure’s reliability and internal structure analyzed from the accompanying openly available data.

## Measurement Quality

To understand a psychological phenomenon you need to be able to accurately capture the relevant constructs. While this premise underlines the core idea behind the use of measures for psychological constructs, it is difficult to guarantee in practice. In general, there are two aspects of a measurement between which we distinguish: validity and reliability. What complicates things is that there are multiple aspects to validity and multiple ways to assess these aspects of validity and reliability. So a researcher needs to know which type of assessment for validity and reliability is important for a measure, and on top of that it can be a complicated task to establish validity and reliability.

Validity is an umbrella term for many different types of validity (construct, predictive, content, internal, external, etc.) and applies to (nearly) all aspects of the research design (CITATIONs INCLUDING VAZIRE et al.). For the purposes of this research we focus on construct validity of the applied measurement, which includes the measure and some aspects of the research design involving the administration of the measure. Construct validity refers to … . It is key to (relevant for nearly all measurement to some extent, because …) … . Evaluating it requires … and …, which in practice means … and … . !!!make sure that this section highlights something about construct validity relevant for our research that most psychologists may not actively realize.!!!

Reliability estimates provide an indication of how consistent the responses on a measurement are. …something about what this consistency is over [might relate to the different types: in CTT it is the correlation between scores on two equivalent forms of the test; but we are more focused on consistency as a basic requirement for an essentially valid measure, because no reliability means no validity]. Reliability is a critical first step to obtaining credible findings. Because if the scores on a measure are not consistent with themselves, it is unlikely that any effect associated with the measure can credibly be established. Psychometrics offers various ways to assess reliability empirically [@nunnally1978overview; @mellenbergh2011conceptual], … test-retest … interrater … internal consistency (this in turn relates back to construct validity)…. [something about the fact that reliability is sample specific and not measurement specific in nearly all cases of us assessing it]

To summarize the previous section, the measurement of a study need to be both valid and reliable to be able to assess the phenomenon of interest. However, recent research has shown that the reliability and validity can often not be discerned from the reported information. Questionable Measurement Practices (QMPs) raise doubts about a measurement’s validity [@flake2020measurement] and have been coined as a term analogous to Questionable Research Practices [QRPs\; @john2012measuring]. QMPs range from lack of transparency and unclear motivation in choice of measure to poor justification for modifications of a measure and procedure of an existing measure [@flake2020measurement].

@flake2022construct documented QMPs among 100 replications and their respective original articles from the RPP [@osc2015estimating]. They coded the number of measures, the number of items in the measure, and the information that was reported describing the measure and justifying its use. They observed limited reporting of evidence demonstrating the reliability and validity of the measurement. Furthermore, auxiliary information on the number of items, the response format, the scoring of the scale, was also not reported for several measures in the RPP. Furthermore, only eight of the 40 translated scales contained validity evidence for the translated version of the scale. Evidence showing that this and other modifications between original and replication did not invalidate the measurement was rare.

!!!Especially worrisome because @shaw2020measurement shows that when running factor analyses on the available data the structural evidence does not always show a good construct validity, so that the lack of reported validity evidence may be hiding psychometrical skeletons in the closet; Reliability something … [Hussey’s work]. !!!

Further findings by  @flake2022construct and others [@flake2017construct; @shaw2020measurement] also show that QMPs not only limit the reported validity of a measurement in a study, the lack of information also creates challenges for replicating researchers. If it is not clear what items were used, how they were scored, and how they were administered, the reconstructed measure used in the replication may be assessing the relevant construct(s) differently, or even assess different construct(s). If different construct(s) are assessed, the replication may not be a test of the same phenomenon as the original. If constructs are assessed differently, the estimated effects in the replication cannot easily be substantially compared to the effects in the original study. In either case, the replication is hardly informative with regards to the phenomenon of interest. Given replication’s importance in cumulative knowledge gain in science, this is worrisome.

## Research Aim

Our aim is to further investigate the reliability, validity, and measurement reporting practices in the Many Labs replications and related original research. We provide a descriptive account of the measurement reporting practices in tandem with the measure’s reliability and validity evidence, obtained from the openly available data from the Many Labs replication projects.

Existing literature has looked at reported reliability, validity, and general measurement features in both original and replication studies before. Previous studies have also recalculated reliabilities from reported information and reanalyzed the validity from original data. Our research provides a unique contribution by combining the reported measurement information in original and replication studies, with reliability and validity re-analyses performed on openly available data from those replication studies, with the added benefit of having data across multiple labs so that variation in reliability and validity across multiple instances can be investigated.

# Disclosures ???Where & How???

@@

## Data Source
The data source is the Many Labs replication projects. These were a series of high profile replication projects wherein multiple psychological studies considered relevant by the community were chosen to be replicated across multiple labs over the world. Practices encountered with measurement in this sample of original articles and replications are a representative reflection of these practices more broadly.

Furthermore, because each study was replicated across multiple labs and the data collected from each lab is publicly available, we can calculate reliability coefficients and perform factor analyses for each measurement across multiple data points and investigate the variance in these estimates.

## Unit of Analysis
Our unit of analysis is a measure of a single psychological construct within a replication protocol/article. Multiple psychological constructs could be measured per original study or replication. We used the replication protocols to identify these measures. We did not include acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses.

## Data Collection
The data consists of three main sources: replication datasets, replication protocols, and original study articles. We retrieved the data of Many Labs 1, 2, 3, & 5 [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many] from their respective OSF pages. Many Labs 4 [@klein2022many] was excluded, as there was no publicly available replication protocol. Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures. We checked the Many Labs data source prior to registering our coding protocol, to check the feasibility of which data could be extracted and how. However, the actual coding took place after registering the coding protocol … Further details can be found in supplement XXX.

### Replication Datasets
The replication datasets refer to the publicly available datasets containing the data obtained from all labs partaking in a Many Labs study. For the analyses, we extracted the scores on the items of each previously identified measure that met our inclusion criteria specified below. When scores could not be clearly identified, any available codebooks, analysis scripts, or study materials were used to identify the relevant scores.

To be included in our reliability recalculations and factor analysis checks, the measure had to be a scale consisting of multiple items. If cleaned data were available, we chose these over raw data, to ensure that variables were coded as intended (e.g., no reverse-coded items). We omitted pilot data from the analyses. These criteria and the nature of the available format(s) of each dataset resulted in suitable item score data from 19 replication sets spread across on average approximately 35 lab locations for our analyses.

@@

### Saving to Intermediate Data Folder
### !!!! OMIT INTERMEDIATE DATA & KEEP FUNCTION THAT REMOVE ALL NON RAW DATA 
### WHEN LOADING THE DATA IN!!!!
saving_to_intermediate_data(data_1.3_clean)
saving_to_intermediate_data(data_1.10_clean)
saving_to_intermediate_data(data_1.11_clean)
saving_to_intermediate_data(data_1.12.3.1_clean)
saving_to_intermediate_data(data_1.12.3.2_clean)
saving_to_intermediate_data(data_2.10.1_clean)
saving_to_intermediate_data(data_2.12.1_clean)
saving_to_intermediate_data(data_2.12.2_clean)
saving_to_intermediate_data(data_2.12.3_clean)
saving_to_intermediate_data(data_2.15_clean)
saving_to_intermediate_data(data_2.20_clean)
saving_to_intermediate_data(data_2.23_clean)
saving_to_intermediate_data(data_3.2.1.1_clean)
saving_to_intermediate_data(data_3.2.1.2_clean)
saving_to_intermediate_data(data_3.7.1_clean)
saving_to_intermediate_data(data_3.7.2_clean)
saving_to_intermediate_data(data_3.8.2_clean)
saving_to_intermediate_data(data_5.1.1_clean)
saving_to_intermediate_data(data_5.1.2_clean)
saving_to_intermediate_data(data_5.4_clean)
saving_to_intermediate_data(data_5.7_clean)
saving_to_intermediate_data(data_5.9.1_clean)
